### 2018-10-01 ms.tex
Add we find to intro.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
malaria is bad but decreasing
moving to strategy of elimination country by country
elimination requires maps of low prevalence areas
but maps in low prevalence areas are difficult
sometimes little data
traditional prevalence mapping won't work
we need new sources of data.

@@

Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihoods for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to an polygon-only disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data.
As case studies we use data from Indonesia, PseudoSenegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point-surveys.

%here we compared 3 models, point only, polygon only and joint models
%we use Madagascar and Indonesia as case studies as they have good %surveillance data and good pr data.
we find that...

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Todo

@@

Here we formulate a joint model that combines polygon incidence data and prevalence point-surveys of \emph{Plasmodium falciparum} using seperate likelihoods for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to a polygon-only, disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains only prevalence point-survey data using data from Indonesia, PseudoSenegal and Madagascar as case studies.
We find that the joint model performs better than the polygon-only model in cases where predictions are needed far from the location of the data or when little data is available for learning relationships between covariates and malaria risk.

%here we compared 3 models, point only, polygon only and joint models
%we use Madagascar and Indonesia as case studies as they have good %surveillance data and good pr data.
